Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-05-01 PaperVictor.tex
Revise manuscript.

\begin{abstract}
We have designed, optimized, fabricated and characterized highly
reflective quasi-omnidirectional (angular range of $0-60^\circ$)
multilayered structures with a wide spectral range. Two techniques,
chirping (a continuous change in thicknesses) and stacking of
Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were carried out employing the
transfer matrix method and we optimized the design parameters to
obtain maximal reflectance averaged over different spectral ranges
for all angles. We fabricated some of the optimized structures with
porous silicon dielectric multilayers with low refractive contrast
and compared their measured  optical properties with the
calculations. Two chirped structures with thicknesses 21.6 $\mu$m
and 60.4 $\mu$m, resulting in quasi-omnidirectional mirrors with
bandwidths of 360 nm and 1800 nm, centered at 1160 nm and 1925 nm
respectively have been shown. In addition, we fabricated a stacked
sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth
of 1800 nm (centered at 1850 nm) and a thickness of 41.5 $\mu$m,
which is almost two third (in thickness) of the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands over different
wavelength ranges. Our analysis techniques can be used for the
optimization of the reflectance not only in multilayered PS
systems  with different refractive index contrasts but also for
systems with other types of materials with low refractive index
contrast. The present study could also be useful for obtaining
omnidirectional dielectric mirrors in large spectral regions using
different materials,  flat focusing reflectors, thermal regulators,
or, if defects are included, as filters or remote
chemical/biosensors with a wide angular independent response.
\end{abstract}

@@

On the other hand, different fabrication techniques have been used to
obtain omnidirectional mirrors (ODM) that operate on the visible and/or
near infrared (Vis-NIR) range of the electromagnetic spectrum. For
example, Chen et al. \cite{Chen1999},
reported the fabrication of a structure made of six pairs of
TiO$_{2}$/SiO$_{2}$  layers with
an omnidirectional band (ODB) of about 70 nm in the NIR range, employing a sol-gel deposition
method. Park et al. \cite{Park2003}, used molecular beam epitaxy to
grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ by selective oxidation of the AlAs
layers, to obtain an ODB from 710 to 950 nm.
On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering for TiO$%
_{2}$ layers and radio frequency magnetron sputtering for SiO$_{2}$
layers to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an ODB from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Use of
porous silicon (PS)
is an attractive alternative, since it can be easily manufactured by
electrochemical etching crystalline Si in an hydrofluoric
acid based electrolyte to obtain a sponge-like nanostructure composed
of Si and air. By modulating the supplied current and its application
time during the electrochemical reaction, it is possible to obtain
multilayered structures allowing for the fabrication ODM's \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
chirped multilayer structures has
increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
PS based dielectric optical filters, quasi-ODM's and ODM's have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} regions.
However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, which makes the
resulting structures relatively fragile. In addition, use of high
porosity makes the fabrication of large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce multilayered mirrors
with high reflectance omnidirectional band
with relatively small thickness and refractive index contrast.

@@

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
        \lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure, and $f(\xi)$ is a smooth function that
goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region, which decreases in
the visible and becomes negligible in the near infrared, so, that the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
        f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
        f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
        \label{F2}
\end{equation}
and%
\begin{equation}
        f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
to maximize the average reflectance $\braket{R}$ over given spectral
and angular ranges. The class
$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
increasing profiles, $f_2$ is the arithmetic mean
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
reflectance for non-polarized light $\braket{R}$ averaged in the
angular range of $0^\circ$ to $90^\circ$ and either in the
spectral region $\mathcal R_1$ from 350 to
1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm.
In the first case, we decided to optimize $\lambda_{min}$ to
obtain the best design in the high absorption zone of the PS.
Approximately $90\%$ of the solar radiation that reaches the
earth's surface is contained in the spectral region
$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \cite{Bird1983}.
A direct
application of the optimized structures in these regions is solar
reflectors. The
optimized parameters corresponding to the choice $p_l=0.51$ and
$p_h=0.76$ for the low and high porosities
are shown in Table \ref{tab:tableA}. In the supplementary
information, we include the parameters used to calculate the
reflectance of structures corresponding to the porosity $p_l=0.30$
and $p_h=0.76$. We also add the theoretical results obtained for
$p_l=0.42$ and $p_h=0.76$.

@@

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM \hl{and quasi-ODM designed to operate in the NIR
region and their (quasi) ODB's are compared with those of
the structures analyzed in the present study. The quasi-ODW}
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
\hl{the quasi-ODB of the structure $S_3$} begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has a quasi-ODW 3.55 times larger. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
\% of the \hl{quasi-ODW of our $S_2$ and $S_3$ structures}. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies
\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
\hl{structures with large quasi-omnidirectional bands with pairs of
materials that have a relatively low refractive index contrast. To be
fair, we have to point out that the (quasi-) omnidirectional band widths of the
structures compared above correspond to different angular ranges,
which are defined by instrumental constrictions.}

@@

We have designed, optimized, fabricated and characterized highly
reflective quasi-omnidirectional (angular range of $0-60^\circ$)
multilayered structures with a wide
spectral range. Two techniques, chirping (a continuous change in thicknesses) and
stacking of Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were
carried out employing the transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
at 1160 nm and 1925 nm respectively have been shown. In addition,
we fabricated a stacked sub-Bragg mirror structure  with a
quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
thickness of 41.5 $\mu$m, which is almost two thirds as thick as the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands
over different wavelength ranges.
Our analysis techniques can
be used for the optimization of the reflectance not only in multilayered PS systems with
different refractive index contrasts but also for systems with other types of
materials with low refractive index contrast. The present study could
also be useful for obtaining omnidirectional dielectric mirrors in
large spectral regions using different materials,  flat focusing
reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.

>>>>

\begin{abstract}
We have designed, optimized, fabricated and characterized highly
reflective quasi-omnidirectional (angular range of $0-60^\circ$)
multilayered structures with a wide spectral range. Two techniques,
chirping (a continuous change in thicknesses) and stacking of
Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were carried out employing the
transfer matrix method and we optimized the design parameters to
obtain maximal reflectance averaged over different spectral ranges
for all angles. We fabricated some of the optimized structures with
porous silicon dielectric multilayers with low refractive contrast
and compared their measured  optical properties with the
calculations. Two chirped structures with thicknesses 21.6 $\mu$m
and 60.4 $\mu$m, resulting in quasi-omnidirectional mirrors with
bandwidths of 360 nm and 1800 nm, centered at 1160 nm and 1925 nm
respectively have been shown. In addition, we fabricated a stacked
sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth
of 1800 nm centered at 1850 nm and a thickness of 41.5 $\mu$m,
which is almost two third (in thickness) of the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands over different
wavelength ranges. Our analysis techniques can be used for the
optimization of the reflectance not only in multilayered PS
systems  with different refractive index contrasts but also for
systems with other types of materials with low refractive index
contrast. The present study could also be useful for obtaining
omnidirectional dielectric mirrors in large spectral regions using
different materials,  flat focusing reflectors, thermal regulators,
or, if defects are included, as filters or remote
chemical/biosensors with a wide angular independent response.
\end{abstract}

@@

On the other hand, different fabrication techniques have been used to
obtain omnidirectional mirrors (ODM) that operate on the visible and/or
near infrared (Vis-NIR) range of the electromagnetic spectrum. For
example, Chen et al. \cite{Chen1999},
reported the fabrication of a structure made of six pairs of
TiO$_{2}$/SiO$_{2}$  layers with
an omnidirectional band (ODB) of about 70 nm in the NIR range, employing a sol-gel deposition
method. Park et al. \cite{Park2003}, used molecular beam epitaxy to
grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ by selective oxidation of the AlAs
layers, to obtain an ODB from 710 to 950 nm.
On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering for TiO$%
_{2}$ layers and radio frequency magnetron sputtering for SiO$_{2}$
layers to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an ODB from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Use of
porous silicon (PS)
is an attractive alternative, since it can be easily manufactured by
electrochemical etching crystalline Si in an hydrofluoric
acid based electrolyte to obtain a sponge-like nanostructure composed
of Si and air. By modulating the supplied current and its application
time during the electrochemical reaction, it is possible to obtain
multilayered structures allowing for the fabrication ODM's \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
chirped multilayer structures has
increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
PS based dielectric optical filters, {\em quasi}-ODM's and ODM's have
been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} regions.
However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, which makes the
resulting structures relatively fragile. In addition, use of high
porosity makes the fabrication of large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce multilayered mirrors
with high reflectance omnidirectional band
with relatively small thickness and refractive index contrast.

@@

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
        \lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure, and $f(\xi)$ is a smooth function that
goes from 0 to 1 as its argument \hl{$\xi=j/(N_p-1)$} goes from the surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region, which decreases in
the visible and becomes negligible in the near infrared, so, that the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
        f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
        f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
        \label{F2}
\end{equation}
and%
\begin{equation}
        f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
to maximize the average reflectance $\braket{R}$ over given spectral
and angular ranges. The class
$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
increasing profiles, $f_2$ is the arithmetic mean
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
reflectance for non-polarized light $\braket{R}$ averaged in the
angular range of $0^\circ$ to $90^\circ$ and either in the
spectral region $\mathcal R_1$ from 350 to
1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm.
In the first case, we decided to optimize $\lambda_{\min}$ to
obtain the best design in the high absorption zone of the PS.
Approximately $90\%$ of the solar radiation that reaches the
earth's surface is contained in the spectral region
$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \cite{Bird1983}.
A direct
application of the optimized structures in these regions is solar
reflectors. The
optimized parameters corresponding to the choice $p_l=0.51$ and
$p_h=0.76$ for the low and high porosities
are shown in Table \ref{tab:tableA}. In the supplementary
information, we include the parameters used to calculate the
reflectance of structures corresponding to the porosity $p_l=0.30$
and $p_h=0.76$. We also add the theoretical results obtained for
$p_l=0.42$ and $p_h=0.76$.

@@

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM's \hl{and quasi-ODM's designed to operate in the NIR
region and their (quasi-) ODB's are compared with those of
the structures analyzed in the present study. The quasi-ODW}
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
\hl{the quasi-ODB of the structure $S_3$} begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has a quasi-ODW 3.55 times larger. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
\% of the \hl{quasi-ODW's of our $S_2$ and $S_3$ structures}. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies
\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
\hl{structures with large quasi-omnidirectional bands with pairs of
materials that have a relatively low refractive index contrast. To be
fair, we have to remark that, as shown in Table \ref{tab:table3}, the
(quasi-) omnidirectional band widths of the structures compared above
correspond to different angular ranges,
which are defined by instrumental constrictions.}

@@

We have designed, optimized, fabricated and characterized highly
reflective quasi-omnidirectional (angular range of $0-60^\circ$)
multilayered structures with a wide
spectral range. Two techniques, chirping (a continuous change in thicknesses) and
stacking of Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were
carried out employing a stabilized transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
at 1160 nm and 1925 nm respectively have been shown. In addition,
we fabricated a stacked sub-Bragg mirror structure  with a
quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
thickness of 41.5 $\mu$m, which is almost two thirds as thick as the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands
over different wavelength ranges.
Our analysis techniques can
be used for the optimization of the reflectance not only in multilayered PS systems with
different refractive index contrasts but also for systems with other types of
materials with low refractive index contrast. The present study could
also be useful for obtaining omnidirectional dielectric mirrors in
large spectral regions using different materials,  flat focusing
reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.
